Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-03 manuscript/manuscript.Rmd

Similarly, although the focus of this paper is on communication in a pricing
context, the techniques explored in this paper (and many of the concerns discussed)
may also be relevant to other contexts, such as claim-level reserving / analytics
or other applications of machine learning to the insurance industry.

@@

This last item raises a final interesting issue. GLMs and their ilk are often 
fitted using one of a handful of standard and well-understood approaches (e.g.,
maximum likelihood estimation). However, this is not possible in general with 
machine learning models, as machine learning algorithms often use loss surfaces 
that are very complex such that it may not be feasible to calculate the global 
minimum of the surface. Certainly, closed form representations of the loss 
surfaces are not generally available. For this reason, the training phase of a 
machine learning model is, in many ways, just as important to one's 
understanding as the model form and the data on which the model is fitted. 
Because the final model result is inseparable from these three components 
(training method, model form, and data), it is not generally adequate to just
know the method employed to make an objective appraisal of the reasonableness 
of the result. More information is necessary.

>>>>

Similarly, although the focus of this paper is on communication in a pricing
context, the techniques explored in this paper (and many of the concerns discussed)
may also be relevant to other contexts, such as claim-level reserving or analytics,
or other applications of machine learning to the insurance industry.

@@

This last item raises a final interesting issue. GLMs and their ilk are often 
fitted using one of a handful of standard and well-understood approaches (e.g.,
maximum likelihood estimation). However, this is not possible in general with 
machine learning models, as machine learning algorithms often use loss surfaces 
that are very complex such that it may not be feasible to calculate the global 
minimum of the surface. Certainly, closed form representations of the loss 
surfaces are not generally available. For this reason, the training phase of a 
machine learning model is, in many ways, just as important to one's 
understanding as the model form and the data on which the model is fitted. 
Because the final model result is inseparable from these three components 
(training method, model form, and data), it is not generally adequate to just
know the method employed to make an objective appraisal of the reasonableness 
of the result.
